On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-03-28 docs/mvfits_paper/mvf.tex
Reorder spin weight qualification [32]

This view currently comes with the added assumption that ${_{-2}}S_{\ell m n} = {_{-2}}Y_{\ell m}$, where ${_{-2}}Y_{\ell m}$ are the spins weighted -2 spherical harmonics.

>>>>

This view currently comes with the added assumption that ${_{-2}}S_{\ell m n} = {_{-2}}Y_{\ell m}$, where ${_{-2}}Y_{\ell m}$ are the spherical harmonics of spin weight -2.
